Re-finding to support a Deep Web Question Answering System

### 2010-03-05 paper/semsearch10/content/nlp.tex
Fixed misspelling

% Joir-dan stuff

When we have completed our Wikipedia corpora from all the blankets in the category hierarchy, our system needs to make sense of the data for execution. The learning process involves the calculation of two n-gram frequency distributions: an n-gram/vocabulary distribution and an n-gram/category distribution. The first value is the count of the individual n-grams in the combined vocabulary of all corpora. The second value is the count of the individual n-grams within a category's blanket. The categories corpora reflect one long context per category, instead of breaking up sentences into different contexts. The idea behind this is that Wikipedia pages are already grouped into categories, that we can assume are related to the topics of each sentence within the corpus. We store distributions, rather than priors, primarily because if at anytime a blanket vocabulary seems inadequate, we can append terms from other sources to both distribution types and recalculate our values. We can simply calculate probabilities and store these separately for the execution of our natural language query engine.

Our goal is to choose that category for use in the SSQ structure. This process requires the tagging and parsing of our natural language query, the extraction of key parts of speech, such as adjectives and nouns, and then using n-gram priors to calculate the appropriate category associated with each term.

Picking out these terms requires knowledge of the structure of the queThe ideal situation would be that we could recognize question patterns, and decide where key information is within the question based upon a given pattern.stion being passed to the system.  Currently, we only work with questions in an answer form, which means there is little to no transformation of the structure, to go from a question to an answer.

Consider the example question: "A 1997 Toyota Corolla needs what size tires?" The answer is: "A 1997 Toyota Corolla needs 17 inch tires."

>>>>

\section{Natural Language Queries}
% Joir-dan stuff
The first step in answering a user query is to determine what, in
fact, is being asked.  Any system that supports user queries places
some constraints on the required input.  These constraints can be
relatively minimal (``Users must type their input on a keyboard in
French.'') or quite constrained (``Users must constuct fully
categorized semi-structured queries employing only those terms and
categories supplied by our database.'')  Our initial goal in Morpheus
is two-fold:

\begin{enumerate}
\item Implement an initial natural language interface that allows
  users to make queries in a loosely constrained English language
  subset.
\item Provide a framework that can support a robust
  interface that employs statistical language processing
  methods.  
\end{enumerate}

At present, we can process English language questions posed in answer
form.  This requires minimal structural transformation in order to
represent the semantic information contained within the question.  We
translate these questions into semi-structured queries that associate
English language terms and modifier phrases with contexts (\emph{who,
  what, when, where})

Input contexts of such a semi-structured query are generally given as
terms (particular dates, names of cars, etc.) while output contexts
are given as categories (tire type, tire size). Thus the inputs of the
user SSQ are uncategorized, while their outputs are categorized.  The
SSQs associated with a QRM are fully categorized (as will be discussed
in section \ref{sec:qrr}). To match a user SSQ to existing QRMs, we
must be able to match their SSQ input and output contexts.  This
requires matching the input terms to their categories, a process we
discuss in section \ref{sec:terms}.
